Advantages of mixed quantum gates for information processing

### 2019-03-18 decorrelation/mixed_unitaries.tex
last bit of tidying section 3 up

As a practical consideration, we would also like to regularize our objective function to enforce sparsity. Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs have non-trivial probability support on a small number of controls. As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}. In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. Thus we would prefer that our solution, if we are forming a $0$MQC, ignores $H_4$. However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'. Thus we would like to be frugal in which controls we select. In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:

\begin{equation}\label{eq:minimization_regularization}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega|| + t\\
&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation} with $\lambda\geq0$. As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be. For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
In both the 0MQC and the 1MQC case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors. Adding this constrain made the 0MQC perform better at the origin by nearly an order of magnitude, and moved the 1MQC from being out-performed by the 0MQC for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls. Imposing this constraint allows us to trade off flatness at the origin for performance. This shows that through adding constraints to our optimization routine, we can make the MQC practically useful. 
\section{Results} % (fold)
\label{sec:results}

>>>>

As a practical consideration, we would also like to regularize our objective function to penalize for non-sparse weightings. Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs only require a small number of controls. As an example, consider Figure \ref{fig:vectorspace}. In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. Thus we would prefer that a $0$MQC, ignore $H_4$. However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives. Thus we would like to be frugal in which controls we select. In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain the one norm of $\omega$ to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:

\begin{equation}\label{eq:minimization_regularization}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega|| + t\\
&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation} with $\lambda\geq0$. As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be. For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
In both the 0MQC and the 1MQC case in our numerical implementation in Section \ref{sub:experimental} we impose the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors. Adding this constraint made the 0MQC perform better at the origin by nearly an order of magnitude, and moved the 1MQC from being out-performed by the 0MQC for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls. Imposing this constraint allows us to trade off flatness at the origin for performance at the origin. This shows that through adding constraints to our optimization routine, we can make the MQC practically useful. 
\section{Results} % (fold)
\label{sec:results}
